Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
WIP on intro + minor other changes

While Henry is lively and always quick at shifting his attention from one
activity to another, Diego is shy and poised. Two very different children,
facing however the same difficulty to write in a legible manner. And, hidden
behind this impaired skill, psycho-social difficulties also arise: they
underperform at school, Henry has to go for follow-up visits to a therapist,
they require ``special care''. This is a source of anxiety, for the children,
and for their parents alike.

@@

Remediations for handwriting difficulties traditionally involve
long interventions (at least 10 weeks~\cite{Hoy2011}), essentially handwriting
training with an occu therapist, and primarly address the motor deficits.
Improvements in self-confidence, anxiety occur (at best) as a consequence of the
child improving his/her handwriting skills and improving his/her performances at
school (when not too late).

We present in this article a new take on this educative challenge, as a
remediation procedure that involve a bad-writer robot that is taught by the
child: by building on the \emph{learning by teaching} paradigm, not only the
child practises hand-writing but, as he/she takes on the role of the teacher,
he/she also positively reinforce his/her self-esteem and motivation (he/she
shifts from the ``underperformer'' to become ``the one who knows and teaches'').

@@

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines~\cite{Rohrbeck2003}. 
To our best knowledge, the application of the paradigm to
handwriting intervention remains, however, unexplored. One reason for this may
due to the requirement of an appropriately unskilled peer for the target child
to tutor, as this may present a logistical constraint if the target child is the
lowest performer in their class.  In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, this
acting is likely to be eventually detected. As such, there is motivation for the
use of a teachable agent which can be configured for a variety of skill levels,
and for which children do not have preconceptions about its handwriting ability.

@@

A robotic learning agent which employs the learning by teaching paradigm has
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out
verbs. The robot is tele-operated and mimics the actions that the children teach
it, but with no long-term memory or learning algorithm in place.  Our project
significantly extends this line of work in two ways. First, by investigating the
context of children's acquisition of a challenging physical skill (handwriting),
and second by proposing a robotic partner which is fully autonomous in its
learning.

@@

Since the child is assumed to take on the role of the teacher, we had to ensure
he/she would be able to manage by him/herself the turn-taking and the overall
progression of the activity (moving to the next letter or word). In our design,
the turn-taking relies on the robot prompting for feedback once it is done with
its writing (simple sentences like ``What do you think?''), and pressing on a
small robot icon on the tablet once the child has finished correcting. In our
experiments, both were easy to grasp for children.

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{experimental_setup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc nao} robot.
        The robot writes on the tactile tablet, the child then corrects the
        robot by directly overwriting its letters on the tablet, with a stylus
        directly. An adult (either a therapist or an experimenter, depending on
        the studies), remains next to the child to guide the work (prompting,
        turn taking, etc.). For some studies, a second tablet and an additional
        camera (dashed) are employed.}

@@

\begin{tikzpicture}[
    >=latex,
    node distance=2cm,
    every edge/.style={draw, very thick},
    redarrow/.style={draw=Red},
    greenarrow/.style={draw=GreenYellow},
    yellowarrow/.style={draw=BurntOrange},
    cmpt/.style={draw, align=center, rounded corners, inner sep=5pt, font=\sf, fill=black!20},
    label/.style={midway, align=left, font=\scriptsize\sf, fill=white, above,opacity=0,text opacity=1}]

@@

The overall architecture of the system (Figure~\ref{fig:archi}) is therefore
spread over several devices: the {\sc nao} robot itself, that we address via
both a ROS API\footnote{The ROS stack for {\sc nao} is available at
\url{http://wiki.ros.org/nao_robot}.} and the Aldebaran-provided NaoQI API, one
to four Android tablets (the main tablet is used to print the robot's letter and
to acquire the children' demonstrations. More tablets have been used in some
studies, either to let the child input words to be written, or for the
experimenter to qualitatively annotate the interaction in a synchronized
fashion), and a central laptop running the machine learning algorithms, the
robot's handwriting gesture generation and high level control of the activity.

>>>>

While Henry is lively and always quick at shifting his attention from one
activity to another, Diego is shy and poised. Two very different children,
facing however the same difficulty to write in a legible manner. And, hidden
beyond this impaired skill, psycho-social difficulties also arise: they
underperform at school, Henry has to go for follow-up visits every week,...
they live under the label ``requires special care''. This is a source of
anxiety, for the children, and for their parents alike.

@@

Remediations for handwriting difficulties traditionally involve long
interventions (at least 10 weeks, \cite{Hoy2011}), essentially consisting in
handwriting training with occupational therapists, and primarily addressing the
\emph{motor} deficits.  Improvements in self-confidence and anxiety occur (at
best) as a side-effect of the child improving his/her handwriting skills and,
consequently, improving his/her performance at school.

We present in this article a new take on this educative challenge, as a
remediation procedure that involve a \emph{bad writer} robot that is taught by the
child: by building on the \emph{learning by teaching} paradigm, not only the
child practises hand-writing but, as (s)he takes on the role of the teacher,
(s)he also positively reinforce his/her self-esteem and motivation: his/her
social role shifts from the ``underperformer'' to ``the one who knows and teaches''.

@@

The \emph{learning by teaching} paradigm, which engages the student in the act
of teaching another, has been shown to produce motivational, meta-cognitive, and
educational benefits in a range of disciplines~\cite{Rohrbeck2003}.  The
application of this paradigm to handwriting intervention remains, however,
unexplored. One reason for this may be due to the requirement of an
appropriately unskilled peer for the child to tutor: it may prove difficult if
the child is the lowest performer in his/her class.  In some cases, it may be
appropriate for a peer or teacher to simulate a na\"ive learner for the target
child to teach. For handwriting however, where one's skill level is visually
evident, this acting is likely to be rapidly detected. This motivates the use of
an artificial teachable agent which can be configured for a variety of skill
levels, and for which children do not have preconceptions about its handwriting
ability.

@@

A robotic learning agent which employs the learning by teaching paradigm has
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out
verbs. The robot is tele-operated (Wizard-Of-Oz) and mimics the actions that the
children teach it, but with no long-term memory or learning algorithm in place.
Our project significantly extends this line of work in two ways. First, by
investigating the context of children's acquisition of a challenging physical
skill (handwriting), and second by proposing a robotic partner which is fully
autonomous in its learning.

@@

Since the child is assumed to take on the role of the teacher, we had to ensure
(s)he would be able to manage by him/herself the turn-taking and the overall
progression of the activity (moving to the next letter or word). In our design,
the turn-taking relies on the robot prompting for feedback once it is done with
its writing (simple sentences like ``What do you think?''), and pressing on a
small robot icon on the tablet once the child has finished correcting. In our
experiments, both were easy to grasp for children.

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{experimental_setup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
        nao} robot.  The robot writes on the tactile tablet, the child then
        corrects the robot by directly overwriting its letters on the tablet
        with a stylus. An adult (either a therapist or an experimenter,
        depending on the studies), remains next to the child to guide the work
        (prompting, turn taking, etc.). For some studies, a second tablet and an
        additional camera (dashed) are employed.}

@@

\begin{tikzpicture}[
    >=latex,
    node distance=2cm,
    every edge/.style={draw, very thick},
    redarrow/.style={draw,red, text=black},
    greenarrow/.style={draw,GreenYellow,text=black},
    yellowarrow/.style={draw,BurntOrange,text=black},
    cmpt/.style={draw, align=center, rounded corners, inner sep=5pt, font=\sf, fill=black!20},
    label/.style={midway, align=left, font=\scriptsize\sf, fill=white, above,opacity=0,text opacity=1}]

@@

The overall architecture of the system (Figure~\ref{fig:archi}) is therefore
spread over several devices: the {\sc nao} robot itself, that we address via
both a ROS API\footnote{The ROS stack for {\sc nao} is available at
\url{http://wiki.ros.org/nao_robot}.} and the Aldebaran-provided NaoQI API, one
to four Android tablets (the main tablet is used to print the robot's letter and
to acquire the children's demonstrations. More tablets have been used in some
studies, either to let the child input words to be written, or for the
experimenter to qualitatively annotate the interaction in a synchronized
fashion), and a central laptop running the machine learning algorithms, the
robot's handwriting gesture generation and high level control of the activity.
